Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every commit to Git and identify which test cases are affected
	regression impact on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be carried out on the evaluation
	performance to identify which changes resulted in the regression
	performance. To find out the root of the problem at the code level, it will be done
	an iterative approach to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Memprediksi tes mana yang dapat memanifestasikan regresi pada level commit.
	Pendekatan ini merupakan kelanjutan dari poin sebelumnya yang mana
	pendekatan dengan melakukan uji pada setiap commit membutuhkan banyak
	sumber daya dan usaha sehingga pendekatan ini akan melakukan prediksi
	secara otomatis apakah sebuah tes akan memanifestasikan regresi kinerja jika
	diberikan sebuah commit kode. Detailnya, pendekatan ini akan mendeteksi apakah
	terdapat regresi pada tes tertentu dari sebuah commit. Untuk membuat model
	prediksi, pertama-tama harus diitenfikasi mana saja tes yang rawan menghasilkan
	regresi dengan mengevaluasi semua tes yang terdampak pada perubahan kode di
	commit sebelumnya dengan menghitung kinerja setiap tes, seperti waktu respon,
	penggunaan CPU dan Memory, pembacaan dan penulisan I/O, dengan melakukan
	setiap tes secara beruntun.
\end{enumerate}

>>>>

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every commit to Git and identify which test cases are affected
	regression impact on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be carried out on the evaluation
	performance to identify which changes resulted in the regression
	performance. To find out the root of the problem at the code level, it will be done
	an iterative approach to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Predict which tests may manifest regression at the commit level.
	This approach is a continuation of the previous point where
	the approach of doing a test on every commit takes a lot
	resources and effort so that this approach will make predictions
	automatically whether a test will manifest a performance regression if
	given a commit code. In detail, this approach will detect whether
	there is a regression on certain tests of a commit. To make a model
	prediction, it must first be identified which tests are prone to yielding
	regression by evaluating all the tests affected by the code change in
	previous commits by calculating the performance of each test, such as response time,
	CPU and Memory usage, I/O reads and writes, by doing
	each test successively.
\end{enumerate}
